%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass[margin, centered, 10.5pt]{res}
\topmargin=-0.5in
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.5in
\itemsep=0in
\parsep=0in
\newsectionwidth{1.1in}
\usepackage[pdftex]{graphicx}
\usepackage{enumitem}
\usepackage{wrapfig}
\usepackage{helvet}
\usepackage[utf8]{inputenc}
\usepackage[colorlinks = false,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\setlength{\textwidth}{6.5in} % Text width of the document
\setlength{\textheight}{720pt}

% \pagestyle{plain} 
% \setcounter{page}{1}
% \pagenumbering{arabic}


\begin{document}
%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------\

\begin{center}
    \hspace{-\hoffset}
    \huge\bf{\href{https://yashhere.github.io}{Yash Agarwal}}
\end{center}
\vspace{-4mm}
\moveleft\hoffset\vbox{\hrule width 19cm height 0.5pt}
\vspace{-7mm}
\begin{center}
    \hspace{-\hoffset}
    \href{mailto:yashagarwaljpr@gmail.com}{yashagarwaljpr@gmail.com} ~\textbullet~ (+91) 9995902061 / (+91) 9928308953
\end{center}
\vspace{-8mm}
\begin{center}
    \hspace{-\hoffset}
    \textbf{Address:} 49-A, Shri Ram Nagar-A, Kalwar Road, Jhotwara, Jaipur, Rajasthan, India - 302012\\
\end{center}
\vspace{-7mm}
\begin{resume}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\section{Education}
\textbf{B.Tech in \href{http://cse.nitc.ac.in}{Computer Science \& Engineering}, Senior Year} \hfill 2014 - Present \\
\href{http://nitc.ac.in/}{National Institute of Technology, Calicut, India}
\begin{itemize}
 \item CGPA of \textbf{7.86}/10 (end of 7\textsuperscript{th} semester)
\end{itemize}
\textbf{High School} - {Jagrati Vidya Mandir, Jhotwara, Jaipur} (RBSE) - 89\% \hfill 2013 \\
\textbf{Secondary School} - Adarsh Vidya Mandir, Jhotwara, Jaipur (RBSE) - 92.5\% \hfill 2011

%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\section{Experience}
\textbf{Web Developer at \href{http://www.meetvaidya.com}{MeetVaidya}} \hfill July, 2015 - December, 2015\\
Worked in a team of 3 to improve the interface of the Web portal for online Ayurvedic consultation using JavaScript, PHP and MySQL.

%----------------------------------------------------------------------------------------
%	Projects Section
%----------------------------------------------------------------------------------------
\section{Projects}
Projects available on GitHub : \url{https://www.github.com/yashhere}
%\setlist[itemize]{
\begin{itemize}[leftmargin=*]
\item \textbf {An Analysis of Android Permission Model} : Proposed as the Final Year Project. Aim is to analyze the Android permission model and to identify various security problems, it poses to normal user.
\item \textbf{\href{https://github.com/yashhere/RedWallDown}{RedWallDown}} : Download trending Reddit wallpapers and set them as wallpaper on your Linux, Mac or Windows machine.
\item \textbf{\href{https://github.com/yashhere/goofy}{Goofy}} : Generate .gitignore file for projects.
\item \textbf{\href{https://github.com/yashhere/BeautifyMP3}{BeautifyMP3}} : A command line tool for fixing ID3 metadata and adding Album Art to MP3 songs.
\item \textbf{\href{https://github.com/yashhere/xkcdTwitterBot}{xkcdTwitterBot}} : A Twitter bot which tweets xkcd comics related to programming, tech, math, algorithms or anything computer science related.
\item \textbf{\href{https://github.com/yashhere/GitView}{GitView}} : A tool to view your GitHub profile in more compact way. Written in Angular.
\item \textbf{\href{https://fosscell.github.io/2017/index.html}{FOSSMeet'17 Marketing Website}} : Developed the marketing website of FOSSMeet'17.
\item \textbf{\href{https://github.com/yashhere/ExperimentalOS}{eXperimental OS}} : Developed a toy OS to understand the internal working of a OS as a part of course project.
% \item \textbf{Linux Kernel Project} : Wrote code for a basic RamDisk Driver using Linux Kernel inbuilt functions and Crypto API to enable encryption and decryption as a part of course project.
% \item \textbf{Seat Jugaad} : Developed a web project for querying train information. Worked in a team of 5 to develop a algorithm for getting alternate routes for a train in case, the complete path is not available in a single journey.
\item \textbf{{Linux From Scratch}} : Built a minimal fully configurable Linux system entirely from source.
\end{itemize}


%----------------------------------------------------------------------------------------
%	TECHNICAL SKILLS SECTION
%----------------------------------------------------------------------------------------
\section{Technical \hspace{2mm} Skills}
%\textbf{Strongest Areas} - Databases, Algorithms, Parallel Programming \\
\textbf{Languages} - C, Python, C++(Basic), Bash(Beginner) \\
\textbf{Tools/Frameworks} - Git, Vim, VisualStudio, SublimeText \\
\textbf{Web Development} - HTML, CSS, JavaScript(Basic), Angular2(Beginner)\\
\textbf{Operating Systems} - Windows, Arch Linux, Ubuntu


%----------------------------------------------------------------------------------------
%	Positions of Responsibility SECTION
%----------------------------------------------------------------------------------------
\section{Positions of \hspace{2mm} Responsibility}
\begin{itemize}[leftmargin=*]
% \item\textbf{Secretary of FOSSCell} \hfill July, 2017 - Present
\item\textbf{{Secretary of \href{https://twitter.com/FOSSCell}{FOSSCell}, NITC}} \hfill July, 2017 - Present
\item\textbf{Lab Admin at \href{http://athena.nitc.ac.in}{Software Systems Lab}} \hfill April, 2016 - Present\\
Maintaining all the Linux based servers of CSE Department and systems of the lab
\item\textbf{Member of FOSSCell, NIT Calicut} \hfill August, 2016 - Present\\
A part of FOSS community at NITC, worked in the organizing team of \href{http://fossmeet.in}{FOSSMeet} 2017.
\item\textbf{Executive at \href{https://www.facebook.com/ipfnitc}{Industrial and Planning Forum}} \hfill April, 2015 - Present\\
Organized techno-managerial events for first year B.Tech students
\end{itemize}

%----------------------------------------------------------------------------------------
%	RELEVANT COURSE SECTION
%----------------------------------------------------------------------------------------
\section{Relevant \hspace{2mm} Courses\\(* Current)}
Data Structures and Algorithms, Foundations of Programming, Computer Organization,\\Operating Systems, Database Management Systems, Computer Architecture, Data Mining,\\Computer Networks, Computational Intelligence, Distributed Computing*, Computer Security*, Natural Language Processing*


%----------------------------------------------------------------------------------------
%	Areas of Interest SECTION
%----------------------------------------------------------------------------------------


\section{Areas of \hspace{2mm} Interest}
Linux System Administration, Server Administration, Computer Networks
% \begin{itemize}[leftmargin=*]
% \item Linux System Administration
% \item Server Administration
% \item Artificial Intelligence
% \item Computer Networks
% \end{itemize}


%----------------------------------------------------------------------------------------
%	Personal Details SECTION
%----------------------------------------------------------------------------------------

% \section{Personal Details}
% \textbf{Father's Name} - Mr. Sarwan Kumar Agarwal \\
% \textbf{DOB} - June 2, 1996 \\
% \textbf{Gender} - Male \\
% \textbf{Martial Status} - Single \\
% \textbf{Permanent Address} - 49-A, Shri Ram Nagar-A, Kalwar Road, Jhotwara, Jaipur, Rajasthan, India 302012\\
% \textbf{Languages} - English, Hindi \\
% \textbf{Hobbies} - Reading Technical Blogs, Reading Quora \\
% \textbf{Strengths} - Quick learner, Team player, Flexible with work \\
% \textbf{Webpage} - \href{https://yashhere.github.io}{https://yashhere.github.io}

%----------------------------------------------------------------------------------------
%	References SECTION
%----------------------------------------------------------------------------------------

% \section{References}

%----------------------------------------------------------------------------------------
%	Declaration SECTION
%----------------------------------------------------------------------------------------

% \section{Declaration}
% I hereby declare that the above information's are true to best of my knowledge.\\[12pt]
% Place: Calicut \hspace{10cm} Signature                                                  

\section{More} 
Please visit \href{https://yashhere.github.io}{https://yashhere.github.io}
\end{resume}
\end{document}